---

title: "ARIMA Modelling of a French Industrial Production Index"


output:
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  message   = FALSE,
  warning   = FALSE,
  fig.align = "center",
  fig.width  = 9,
  fig.height = 5
)
```

```{r packages}
pkgs <- c("tseries", "forecast", "urca")
for (p in pkgs) if (!requireNamespace(p, quietly = TRUE)) install.packages(p)

library(tseries)
library(forecast)
library(urca)
```

---

# Part I – The Data

## Question 1 – Description of the selected series

### Importing the data

The data are imported from the CSV files downloaded from the INSEE databank.
The zip archive is automatically extracted if the files are not already present.

```{r import-data}
data_file <- "valeurs_mensuelles.csv"
meta_file <- "caractéristiques.csv"

# Verification
if (!file.exists(data_file)) stop("valeurs_mensuelles.csv not found")
if (!file.exists(meta_file)) stop("caractéristiques.csv not found")


# --- Metadata ---
metadata <- read.csv(
  meta_file,
  sep = ";", header = TRUE, nrows = 1,
  fileEncoding = "UTF-8-BOM", stringsAsFactors = FALSE,
  colClasses = "character", check.names = FALSE
)
names(metadata) <- sub("^\ufeff", "", names(metadata))

# --- Series values ---
raw <- read.csv(
  data_file,
  sep = ";", header = FALSE, skip = 4,
  fileEncoding = "UTF-8-BOM", stringsAsFactors = FALSE,
  colClasses = "character"
)
names(raw) <- c("period", "value", "code")
raw <- raw[grepl("^[0-9]{4}-[0-9]{2}$", raw$period), ]
raw$value <- as.numeric(gsub(",", ".", raw$value))
raw$date  <- as.Date(paste0(raw$period, "-01"))
raw       <- raw[order(raw$date), ]

head(raw, 3)
tail(raw, 3)
```

### Dynamic summary table

```{r summary-table}
summary_table <- data.frame(
  Attribute = c("idBank", "Indicator", "Activity", "Correction",
                "Geography", "Base", "Frequency",
                "Start", "End", "Observations", "Missing values",
                "Min", "Mean", "Max"),
  Value = c(
    metadata$idBank,
    metadata$Indicateur,
    metadata$Activité,
    metadata$Correction,
    metadata$`Zone géographique`,
    metadata$`Base de l'indice`,
    metadata$Périodicité,
    raw$period[1],
    raw$period[nrow(raw)],
    as.character(nrow(raw)),
    as.character(sum(is.na(raw$value))),
    as.character(round(min(raw$value,  na.rm = TRUE), 2)),
    as.character(round(mean(raw$value, na.rm = TRUE), 2)),
    as.character(round(max(raw$value,  na.rm = TRUE), 2))
  )
)

summary_table
```

### Build the `ts` object

```{r build-ts}
start_year  <- as.integer(format(raw$date[1], "%Y"))
start_month <- as.integer(format(raw$date[1], "%m"))

Y <- ts(raw$value,
        start     = c(start_year, start_month),
        frequency = 12)

T <- length(Y)
cat("Series length  T =", T, "observations\n")
cat("Period:", format(time(Y)[1]), "to", format(time(Y)[T]), "\n")
```

### Description

The selected series is the **Industrial Production Index (IPI), seasonally and
working-day adjusted (CVS-CJO)**, for the sector *"Autres industries
extractives"* (NAF revision 2, **division 08**). This division covers the
extraction of non-energy minerals such as stone, sand, gravel, chalk, clay,
and salt.

The sample runs from `r raw$period[1]` to `r raw$period[nrow(raw)]`, yielding
**`r T` monthly observations** — well above the 100-observation minimum
required by the assignment. There are **no missing values** in the sample.

**Seasonal adjustment.** The CVS-CJO correction is applied upstream by INSEE,
so the series is already free of seasonal fluctuations and calendar effects.
No additional seasonal decomposition is needed.

**Logarithmic transformation.** The series is strictly positive, so a log
transformation is technically feasible. We apply it for two reasons: (i) it
stabilises the variance if the latter scales with the level, and (ii) after
first-differencing, $X_t = \Delta \log Z_t$ is directly interpretable as an
approximate monthly growth rate of industrial production. We verify the
relevance of this choice in Question 2 through formal stationarity tests.

---

## Question 2 – Transformation toward stationarity

### Applied transformation

We apply the log transformation followed by a first difference:

$$X_t = \Delta \log Z_t = \log Z_t - \log Z_{t-1}$$

where $Z_t$ is the original IPI. The series $X_t$ represents the approximate
monthly growth rate of industrial production (in log points).

```{r transformation}
log_Y <- log(Y)          # log-level
X     <- diff(log_Y)     # working series: Xt = Δ log(Zt)
X_pct <- 100 * X         # expressed in percent for readability

cat("Length of Xt:", length(X), "observations\n")
```

### Descriptive comparison across transformations

```{r transfo-summary}
half_stats <- function(series, label) {
  v <- as.numeric(series); n <- length(v)
  h1 <- v[1:floor(n/2)]; h2 <- v[(floor(n/2)+1):n]
  data.frame(
    Series          = label,
    Mean            = round(mean(v),  4),
    Std_dev         = round(sd(v),    4),
    Mean_1st_half   = round(mean(h1), 4),
    Mean_2nd_half   = round(mean(h2), 4),
    Sd_1st_half     = round(sd(h1),   4),
    Sd_2nd_half     = round(sd(h2),   4)
  )
}

rbind(
  half_stats(Y,     "Original index Zt"),
  half_stats(log_Y, "Log index log(Zt)"),
  half_stats(X,     "Delta log index Xt")
)
```

The original index shows a large gap between the first-half mean (~110) and the
second-half mean (~85), confirming a persistent downward drift. After the log
and first difference, the two half-sample means are close to zero and the
standard deviations are similar — a first indication that $X_t$ is stationary.

### Formal unit-root tests — raw log-level series

```{r adf-raw}
cat("--- Augmented Dickey-Fuller test (log-level) ---\n")
adf.test(log_Y, alternative = "stationary")
```

```{r kpss-raw}
cat("--- KPSS test, null: level stationarity (log-level) ---\n")
kpss.test(log_Y, null = "Level")

cat("\n--- KPSS test, null: trend stationarity (log-level) ---\n")
kpss.test(log_Y, null = "Trend")
```

**Interpretation:**

- **ADF:** the unit-root null *cannot* be rejected (p-value > 0.05) — the
  log-level series is consistent with an integrated process.
- **KPSS (level):** level-stationarity is *strongly rejected* (p-value < 0.01).
- **KPSS (trend):** trend-stationarity is *also rejected*, ruling out a purely
  deterministic trend as the sole source of non-stationarity.

The log-level series contains a **stochastic trend (unit root)**. Correcting a
deterministic trend alone would not be sufficient; first differencing is the
appropriate transformation.

### Formal unit-root tests — differenced series $X_t$

```{r adf-diff}
cat("--- ADF test (Xt = Δ log Zt) ---\n")
adf.test(X, alternative = "stationary")
```

```{r kpss-diff}
cat("--- KPSS test, null: level stationarity (Xt) ---\n")
kpss.test(X, null = "Level")
```

**Interpretation:**

- **ADF:** the unit-root null is *strongly rejected* (p-value < 0.01) — $X_t$
  is stationary.
- **KPSS:** level-stationarity is *not rejected* (p-value > 0.05), confirming
  stationarity.

Both tests agree: **one differencing of the log is sufficient**. We set
**d = 1** and do not difference further, as over-differencing would inflate the
variance and induce unnecessary MA components in the model.

---

## Question 3 – Graphical representation before and after transformation

### Raw series $Z_t$

```{r plot-raw, fig.height=4.5}
plot(Y,
     main = "Industrial Production Index – Other Mining and Quarrying  [raw series Zt]",
     ylab = "Index (base 100 = 2021)",
     xlab = "",
     col  = "#1F4E79",
     lwd  = 2)
abline(h = mean(Y), col = "#B91C1C", lty = 2, lwd = 1.5)
legend("topright",
       legend = c("Observed series Zt", "Sample mean"),
       col    = c("#1F4E79", "#B91C1C"),
       lty    = c(1, 2), lwd = c(2, 1.5), bty = "n")
grid()
```

### Log-level series $\log Z_t$

```{r plot-log, fig.height=4.5}
plot(log_Y,
     main = "Log of the IPI  [log(Zt)]",
     ylab = "Log index",
     xlab = "",
     col  = "#7A3E9D",
     lwd  = 2)
grid()
```

The log transformation compresses extreme values and will make the first
difference interpretable as a growth rate, but it does not remove the downward
trend — this series remains non-stationary.

### ACF and PACF of the log-level series

```{r acf-raw, fig.height=4.5}
par(mfrow = c(1, 2))
acf (log_Y, lag.max = 48, main = "ACF – log-level log(Zt)")
pacf(log_Y, lag.max = 48, main = "PACF – log-level log(Zt)")
par(mfrow = c(1, 1))
```

The ACF decays extremely slowly and remains significant over many lags — a
textbook signature of a unit root. The PACF cuts off sharply after lag 1,
typical of an AR(1)-like integrated process.

### Differenced series $X_t = \Delta \log Z_t$

```{r plot-diff, fig.height=4.5}
plot(X_pct,
     main = "Stationary transformation: 100 × Δ log(Zt)  [working series Xt]",
     ylab = "Approximate monthly growth rate (%)",
     xlab = "",
     col  = "#0F766E",
     lwd  = 1.5)
abline(h = mean(X_pct), col = "#B91C1C", lty = 2, lwd = 1.5)
legend("topright",
       legend = c("Xt = 100 × Δ log(Zt)", "Sample mean"),
       col    = c("#0F766E", "#B91C1C"),
       lty    = c(1, 2), lwd = c(1.5, 1.5), bty = "n")
grid()
```

### ACF and PACF of the differenced series

```{r acf-diff, fig.height=4.5}
par(mfrow = c(1, 2))
acf (X, lag.max = 36, main = "ACF – differenced series Xt")
pacf(X, lag.max = 36, main = "PACF – differenced series Xt")
par(mfrow = c(1, 1))
```

**Comments.** After the log-difference transformation, the series oscillates
around zero with no visible trend. Variance is roughly stable over time, with
slightly higher volatility around the 2008–2009 financial crisis and the 2020
Covid-19 shock — episodic events that do not invalidate stationarity. The ACF
of $X_t$ drops quickly to near zero, and the PACF shows only one or two
significant spikes, consistent with a **low-order stationary ARMA process**.
This confirms that $X_t$ is ready for ARMA modelling in Part II.

---

## Conclusion of Part I

The selected INSEE series satisfies all assignment requirements: it is a French
monthly aggregate IPI, seasonally and working-day adjusted, with
**`r T` observations** and no missing values. The series contains a stochastic
trend confirmed by ADF and KPSS tests, so we apply a log transformation
followed by a first difference. The working series for the rest of the
assignment is:

$$\boxed{X_t = \Delta \log Z_t = \log Z_t - \log Z_{t-1}}$$

This series is interpreted as the monthly growth rate of industrial production
in the Other Mining and Quarrying sector, and its stationarity has been
verified both graphically and through formal unit-root tests.

---

## Part II — ARIMA Grid Search (Box‑Jenkins)

We now run a full grid search over ARMA orders using the working series `X` (the
first-differenced log series defined above). The grid covers p = 0..5 and q = 0..2
and uses `d = 0` because `X` is already a first difference of the log-level.

```{r arima-grid, echo=TRUE}



# Parameters
p_max <- 5
q_max <- 2
d_ord <- 0   # X is already differenced: Δ log(Z)

stopifnot(exists("X"))
y_series <- as.numeric(X)

results <- list()

for (p in 0:p_max) {
  for (q in 0:q_max) {
    cat(sprintf("Fitting ARIMA(%d,%d,%d) on X ...\n", p, d_ord, q))
    fit <- tryCatch({
      stats::arima(y_series, order = c(p, d_ord, q), method = "ML")
    }, error = function(e) {
      cat("  -> error: ", conditionMessage(e), "\n")
      return(NULL)
    })
    if (is.null(fit)) {
      results[[length(results) + 1]] <- data.frame(p = p, q = q, converged = FALSE,
                                                   last_ar_pval = NA_real_, last_ma_pval = NA_real_,
                                                   ljung_pval = NA_real_, AIC = NA_real_, BIC = NA_real_,
                                                   stringsAsFactors = FALSE)
      next
    }

    coefs <- coef(fit)
    vc <- tryCatch({ fit$var.coef }, error = function(e) NULL)
    se <- if (!is.null(vc) && is.matrix(vc)) sqrt(diag(vc)) else rep(NA_real_, length(coefs))
    names(se) <- names(coefs)

    last_ar_pval <- NA_real_
    if (p > 0) {
      ar_names <- grep("^ar", names(coefs), value = TRUE)
      if (length(ar_names) >= p) {
        last_ar_name <- ar_names[p]
        if (!is.na(se[last_ar_name])) {
          tval <- coefs[last_ar_name] / se[last_ar_name]
          last_ar_pval <- 2 * (1 - pnorm(abs(tval)))
        }
      }
    }

    last_ma_pval <- NA_real_
    if (q > 0) {
      ma_names <- grep("^ma", names(coefs), value = TRUE)
      if (length(ma_names) >= q) {
        last_ma_name <- ma_names[q]
        if (!is.na(se[last_ma_name])) {
          tval <- coefs[last_ma_name] / se[last_ma_name]
          last_ma_pval <- 2 * (1 - pnorm(abs(tval)))
        }
      }
    }

    resid <- as.numeric(residuals(fit))
    lb <- tryCatch({ stats::Box.test(resid, type = "Ljung-Box", lag = 12, fitdf = p + q) }, error = function(e) NULL)
    ljung_pval <- if (!is.null(lb)) lb$p.value else NA_real_

    aic <- AIC(fit)
    nobs <- length(na.omit(resid))
    bic <- if (!is.na(aic)) AIC(fit, k = log(nobs)) else NA_real_

    results[[length(results) + 1]] <- data.frame(p = p, q = q, converged = TRUE,
                                                 last_ar_pval = last_ar_pval, last_ma_pval = last_ma_pval,
                                                 ljung_pval = ljung_pval, AIC = aic, BIC = bic,
                                                 stringsAsFactors = FALSE)
  }
}

res_df <- do.call(rbind, results)
res_df$valid_coeffs <- with(res_df, (is.na(last_ar_pval) | last_ar_pval < 0.05) & (is.na(last_ma_pval) | last_ma_pval < 0.05))
res_df$white_resid <- res_df$ljung_pval > 0.05
res_df <- res_df[order(res_df$AIC), ]

write.csv(res_df, file = "arima_grid_results_X.csv", row.names = FALSE)

cat("\nTop models by AIC:\n")
print(head(res_df, 10))

best_row <- res_df[1, ]
cat(sprintf("\nBest model by AIC: ARIMA(%d,%d,%d)\n", best_row$p, 0, best_row$q))

if (!is.na(best_row$AIC)) {
  best_fit <- tryCatch({ stats::arima(y_series, order = c(best_row$p, 0, best_row$q), method = "ML") }, error = function(e) NULL)
  if (!is.null(best_fit)) saveRDS(best_fit, file = "best_arima_X.rds")
}

cat("\nSaved results to arima_grid_results_X.csv and best_arima_X.rds (if estimated).\n")
```



---

*End of Part I*
