---

title: "ARIMA Modelling of a French Industrial Production Index"


output:
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  message   = FALSE,
  warning   = FALSE,
  fig.align = "center",
  fig.width  = 9,
  fig.height = 5
)
```

```{r packages}
pkgs <- c("tseries", "forecast", "urca", "lmtest")
for (p in pkgs) if (!requireNamespace(p, quietly = TRUE)) install.packages(p)

library(tseries)
library(forecast)
library(urca)
library(lmtest)
```

---

# Part I – The Data

## Question 1 – Description of the selected series

### Importing the data

The data are imported from the CSV files downloaded from the INSEE databank.
The zip archive is automatically extracted if the files are not already present.

```{r import-data}
data_file <- "valeurs_mensuelles.csv"
meta_file <- "caractéristiques.csv"


# Verification
if (!file.exists(data_file)) stop("valeurs_mensuelles.csv not found")
if (!file.exists(meta_file)) stop("caractéristiques.csv not found")


# --- Metadata ---
metadata <- read.csv(
  meta_file,
  sep = ";", header = TRUE, nrows = 1,
  fileEncoding = "UTF-8-BOM", stringsAsFactors = FALSE,
  colClasses = "character", check.names = FALSE
)
names(metadata) <- sub("^\ufeff", "", names(metadata))

# --- Series values ---
raw <- read.csv(
  data_file,
  sep = ";", header = FALSE, skip = 4,
  fileEncoding = "UTF-8-BOM", stringsAsFactors = FALSE,
  colClasses = "character"
)
names(raw) <- c("period", "value", "code")
raw <- raw[grepl("^[0-9]{4}-[0-9]{2}$", raw$period), ]
raw$value <- as.numeric(gsub(",", ".", raw$value))
raw$date  <- as.Date(paste0(raw$period, "-01"))
raw       <- raw[order(raw$date), ]

head(raw, 3)
tail(raw, 3)
```

### Dynamic summary table

```{r summary-table}
summary_table <- data.frame(
  Attribute = c("idBank", "Indicator", "Activity", "Correction",
                "Geography", "Base", "Frequency",
                "Start", "End", "Observations", "Missing values",
                "Min", "Mean", "Max"),
  Value = c(
    metadata$idBank,
    metadata$Indicateur,
    metadata$Activité,
    metadata$Correction,
    metadata$`Zone géographique`,
    metadata$`Base de l'indice`,
    metadata$Périodicité,
    raw$period[1],
    raw$period[nrow(raw)],
    as.character(nrow(raw)),
    as.character(sum(is.na(raw$value))),
    as.character(round(min(raw$value,  na.rm = TRUE), 2)),
    as.character(round(mean(raw$value, na.rm = TRUE), 2)),
    as.character(round(max(raw$value,  na.rm = TRUE), 2))
  )
)

summary_table
```

### Build the `ts` object

```{r build-ts}
start_year  <- as.integer(format(raw$date[1], "%Y"))
start_month <- as.integer(format(raw$date[1], "%m"))

Y <- ts(raw$value,
        start     = c(start_year, start_month),
        frequency = 12)

T <- length(Y)
cat("Series length  T =", T, "observations\n")
cat("Period:", format(time(Y)[1]), "to", format(time(Y)[T]), "\n")
```

### Description

The selected series is the **Industrial Production Index (IPI), seasonally and
working-day adjusted (CVS-CJO)**, for the sector *"Autres industries
extractives"* (NAF revision 2, **division 08**). This division covers the
extraction of non-energy minerals such as stone, sand, gravel, chalk, clay,
and salt.

The sample runs from `r raw$period[1]` to `r raw$period[nrow(raw)]`, yielding
**`r T` monthly observations** — well above the 100-observation minimum
required by the assignment. There are **no missing values** in the sample.

**Seasonal adjustment.** The CVS-CJO correction is applied upstream by INSEE,
so the series is already free of seasonal fluctuations and calendar effects.
No additional seasonal decomposition is needed.

**Logarithmic transformation.** The series is strictly positive, so a log
transformation is technically feasible. We apply it for two reasons: (i) it
stabilises the variance if the latter scales with the level, and (ii) after
first-differencing, $X_t = \Delta \log Z_t$ is directly interpretable as an
approximate monthly growth rate of industrial production. We verify the
relevance of this choice in Question 2 through formal stationarity tests.

---

## Question 2 – Transformation toward stationarity

### Applied transformation

We apply the log transformation followed by a first difference:

$$X_t = \Delta \log Z_t = \log Z_t - \log Z_{t-1}$$

where $Z_t$ is the original IPI. The series $X_t$ represents the approximate
monthly growth rate of industrial production (in log points).

```{r transformation}
log_Y <- log(Y)          # log-level
X     <- diff(log_Y)     # working series: Xt = Δ log(Zt)
X_pct <- 100 * X         # expressed in percent for readability

cat("Length of Xt:", length(X), "observations\n")
```

### Descriptive comparison across transformations

```{r transfo-summary}
half_stats <- function(series, label) {
  v <- as.numeric(series); n <- length(v)
  h1 <- v[1:floor(n/2)]; h2 <- v[(floor(n/2)+1):n]
  data.frame(
    Series          = label,
    Mean            = round(mean(v),  4),
    Std_dev         = round(sd(v),    4),
    Mean_1st_half   = round(mean(h1), 4),
    Mean_2nd_half   = round(mean(h2), 4),
    Sd_1st_half     = round(sd(h1),   4),
    Sd_2nd_half     = round(sd(h2),   4)
  )
}

rbind(
  half_stats(Y,     "Original index Zt"),
  half_stats(log_Y, "Log index log(Zt)"),
  half_stats(X,     "Delta log index Xt")
)
```

The original index shows a large gap between the first-half mean (~110) and the
second-half mean (~85), confirming a persistent downward drift. After the log
and first difference, the two half-sample means are close to zero and the
standard deviations are similar — a first indication that $X_t$ is stationary.

### Formal unit-root tests — raw log-level series

```{r adf-raw}
cat("--- Augmented Dickey-Fuller test (log-level) ---\n")
adf.test(log_Y, alternative = "stationary")
```

```{r kpss-raw}
cat("--- KPSS test, null: level stationarity (log-level) ---\n")
kpss.test(log_Y, null = "Level")

cat("\n--- KPSS test, null: trend stationarity (log-level) ---\n")
kpss.test(log_Y, null = "Trend")
```

**Interpretation:**

- **ADF:** the unit-root null *cannot* be rejected (p-value > 0.05) — the
  log-level series is consistent with an integrated process.
- **KPSS (level):** level-stationarity is *strongly rejected* (p-value < 0.01).
- **KPSS (trend):** trend-stationarity is *also rejected*, ruling out a purely
  deterministic trend as the sole source of non-stationarity.

The log-level series contains a **stochastic trend (unit root)**. Correcting a
deterministic trend alone would not be sufficient; first differencing is the
appropriate transformation.

### Formal unit-root tests — differenced series $X_t$

```{r adf-diff}
cat("--- ADF test (Xt = Δ log Zt) ---\n")
adf.test(X, alternative = "stationary")
```

```{r kpss-diff}
cat("--- KPSS test, null: level stationarity (Xt) ---\n")
kpss.test(X, null = "Level")
```

**Interpretation:**

- **ADF:** the unit-root null is *strongly rejected* (p-value < 0.01) — $X_t$
  is stationary.
- **KPSS:** level-stationarity is *not rejected* (p-value > 0.05), confirming
  stationarity.

Both tests agree: **one differencing of the log is sufficient**. We set
**d = 1** and do not difference further, as over-differencing would inflate the
variance and induce unnecessary MA components in the model.

---

## Question 3 – Graphical representation before and after transformation

### Raw series $Z_t$

```{r plot-raw, fig.height=4.5}
plot(Y,
     main = "Industrial Production Index – Other Mining and Quarrying  [raw series Zt]",
     ylab = "Index (base 100 = 2021)",
     xlab = "",
     col  = "#1F4E79",
     lwd  = 2)
abline(h = mean(Y), col = "#B91C1C", lty = 2, lwd = 1.5)
legend("topright",
       legend = c("Observed series Zt", "Sample mean"),
       col    = c("#1F4E79", "#B91C1C"),
       lty    = c(1, 2), lwd = c(2, 1.5), bty = "n")
grid()
```

### Log-level series $\log Z_t$

```{r plot-log, fig.height=4.5}
plot(log_Y,
     main = "Log of the IPI  [log(Zt)]",
     ylab = "Log index",
     xlab = "",
     col  = "#7A3E9D",
     lwd  = 2)
grid()
```

The log transformation compresses extreme values and will make the first
difference interpretable as a growth rate, but it does not remove the downward
trend — this series remains non-stationary.

### ACF and PACF of the log-level series

```{r acf-raw, fig.height=4.5}
par(mfrow = c(1, 2))
acf (log_Y, lag.max = 48, main = "ACF – log-level log(Zt)")
pacf(log_Y, lag.max = 48, main = "PACF – log-level log(Zt)")
par(mfrow = c(1, 1))
```

The ACF decays extremely slowly and remains significant over many lags — a
textbook signature of a unit root. The PACF cuts off sharply after lag 1,
typical of an AR(1)-like integrated process.

### Differenced series $X_t = \Delta \log Z_t$

```{r plot-diff, fig.height=4.5}
plot(X_pct,
     main = "Stationary transformation: 100 × Δ log(Zt)  [working series Xt]",
     ylab = "Approximate monthly growth rate (%)",
     xlab = "",
     col  = "#0F766E",
     lwd  = 1.5)
abline(h = mean(X_pct), col = "#B91C1C", lty = 2, lwd = 1.5)
legend("topright",
       legend = c("Xt = 100 × Δ log(Zt)", "Sample mean"),
       col    = c("#0F766E", "#B91C1C"),
       lty    = c(1, 2), lwd = c(1.5, 1.5), bty = "n")
grid()
```

### ACF and PACF of the differenced series

```{r acf-diff, fig.height=4.5}
par(mfrow = c(1, 2))
acf (X, lag.max = 36, main = "ACF – differenced series Xt")
pacf(X, lag.max = 36, main = "PACF – differenced series Xt")
par(mfrow = c(1, 1))
```

**Comments.** After the log-difference transformation, the series oscillates
around zero with no visible trend. Variance is roughly stable over time, with
slightly higher volatility around the 2008–2009 financial crisis and the 2020
Covid-19 shock — episodic events that do not invalidate stationarity. The ACF
of $X_t$ drops quickly to near zero, and the PACF shows only one or two
significant spikes, consistent with a **low-order stationary ARMA process**.
This confirms that $X_t$ is ready for ARMA modelling in Part II.

---

## Conclusion of Part I

The selected INSEE series satisfies all assignment requirements: it is a French
monthly aggregate IPI, seasonally and working-day adjusted, with
**`r T` observations** and no missing values. The series contains a stochastic
trend confirmed by ADF and KPSS tests, so we apply a log transformation
followed by a first difference. The working series for the rest of the
assignment is:

$$\boxed{X_t = \Delta \log Z_t = \log Z_t - \log Z_{t-1}}$$

This series is interpreted as the monthly growth rate of industrial production
in the Other Mining and Quarrying sector, and its stationarity has been
verified both graphically and through formal unit-root tests.

---

## Part II — ARIMA Grid Search (Box‑Jenkins)

We now run a full grid search over ARMA orders using the working series `X` (the
first-differenced log series defined above). The grid covers p = 0..5 and q = 0..2
and uses `d = 0` because `X` is already a first difference of the log-level.
The upper bound q = 2 is chosen because the ACF of \(X_t\) shows short-run
spikes mainly at lags 1 and 2.

```{r arima-grid, echo=TRUE}



# Parameters
p_max <- 5
q_max <- 2
d_ord <- 0   # X is already differenced: Δ log(Z)

stopifnot(exists("X"))
y_series <- as.numeric(X)

results <- list()

for (p in 0:p_max) {
  for (q in 0:q_max) {
    cat(sprintf("Fitting ARIMA(%d,%d,%d) on X ...\n", p, d_ord, q))
    fit <- tryCatch({
      stats::arima(
        y_series,
        order = c(p, d_ord, q),
        include.mean = FALSE,
        method = "ML"
      )
    }, error = function(e) {
      cat("  -> error: ", conditionMessage(e), "\n")
      return(NULL)
    })
    if (is.null(fit)) {
      results[[length(results) + 1]] <- data.frame(p = p, q = q, converged = FALSE,
                                                   last_ar_pval = NA_real_, last_ma_pval = NA_real_,
                                                   ljung_pval = NA_real_, AIC = NA_real_, BIC = NA_real_,
                                                   stringsAsFactors = FALSE)
      next
    }

    coefs <- coef(fit)
    vc <- tryCatch({ fit$var.coef }, error = function(e) NULL)
    se <- if (!is.null(vc) && is.matrix(vc)) sqrt(diag(vc)) else rep(NA_real_, length(coefs))
    names(se) <- names(coefs)

    last_ar_pval <- NA_real_
    if (p > 0) {
      ar_names <- grep("^ar", names(coefs), value = TRUE)
      if (length(ar_names) >= p) {
        last_ar_name <- ar_names[p]
        if (!is.na(se[last_ar_name])) {
          tval <- coefs[last_ar_name] / se[last_ar_name]
          last_ar_pval <- 2 * (1 - pnorm(abs(tval)))
        }
      }
    }

    last_ma_pval <- NA_real_
    if (q > 0) {
      ma_names <- grep("^ma", names(coefs), value = TRUE)
      if (length(ma_names) >= q) {
        last_ma_name <- ma_names[q]
        if (!is.na(se[last_ma_name])) {
          tval <- coefs[last_ma_name] / se[last_ma_name]
          last_ma_pval <- 2 * (1 - pnorm(abs(tval)))
        }
      }
    }

    resid <- as.numeric(residuals(fit))
    lb <- tryCatch({ stats::Box.test(resid, type = "Ljung-Box", lag = 20, fitdf = p + q) }, error = function(e) NULL)
    ljung_pval <- if (!is.null(lb)) lb$p.value else NA_real_

    aic <- AIC(fit)
    nobs <- length(na.omit(resid))
    bic <- if (!is.na(aic)) AIC(fit, k = log(nobs)) else NA_real_

    results[[length(results) + 1]] <- data.frame(p = p, q = q, converged = TRUE,
                                                 last_ar_pval = last_ar_pval, last_ma_pval = last_ma_pval,
                                                 ljung_pval = ljung_pval, AIC = aic, BIC = bic,
                                                 stringsAsFactors = FALSE)
  }
}

res_df <- do.call(rbind, results)

# A model is valid only if the highest-order AR/MA coefficients are significant.
res_df$valid_coeffs <- with(
  res_df,
  (p == 0 | (!is.na(last_ar_pval) & last_ar_pval < 0.05)) &
    (q == 0 | (!is.na(last_ma_pval) & last_ma_pval < 0.05))
)

# Residuals must behave as white noise.
res_df$white_resid <- !is.na(res_df$ljung_pval) & res_df$ljung_pval > 0.05

# Keep only valid Box-Jenkins candidates.
valid_models <- res_df[
  res_df$converged == TRUE &
    res_df$valid_coeffs == TRUE &
    res_df$white_resid == TRUE,
]

# Rank valid models by AIC.
valid_models <- valid_models[order(valid_models$AIC), ]

if (nrow(valid_models) == 0) {
  stop("No valid model found. Relax filter criteria.")
}

write.csv(res_df, file = "arima_grid_results_X.csv", row.names = FALSE)
write.csv(valid_models, file = "valid_arima_models_X.csv", row.names = FALSE)

cat("\nTop valid models by AIC:\n")
print(head(valid_models, 10))

best_row <- valid_models[1, ]

cat(sprintf(
  "\nBest valid model by AIC: ARMA(%d,%d) on X\n",
  best_row$p, best_row$q
))

best_fit <- stats::arima(
  y_series,
  order = c(best_row$p, 0, best_row$q),
  include.mean = FALSE,
  method = "ML"
)

print(best_fit)
saveRDS(best_fit, file = "best_arima_X.rds")

cat("\nSaved full grid, valid models, and best model.\n")
```

## Question 4 – ARMA Model Selection, Estimation and Validation

The stationary series used for ARMA modelling is \(X_t = \Delta \log Z_t\).
We estimate ARMA(p,q) models with \(p = 0,\ldots,5\) and \(q = 0,\ldots,2\).
The final choice is made in three steps: first, the highest-order AR and MA
coefficients must be statistically significant; second, the Ljung-Box test must
not reject the absence of residual autocorrelation; third, among the valid
models, we select the model with the lowest AIC.

The best model among the valid candidates is an ARMA(0,2). Although ARMA(2,1)
has a slightly lower AIC when all models are considered, it is not retained
because its highest-order AR coefficient is not significant. The ARMA(0,2)
model is therefore preferred because it is valid, parsimonious, and has
white-noise residuals.

The model is estimated without a constant because \(X_t\) is a log-differenced
series with a mean close to zero, and the intercept is not significant when it
is included. The estimated ARMA(0,2) model is:

\[
X_t = \varepsilon_t + \theta_1 \varepsilon_{t-1}
      + \theta_2 \varepsilon_{t-2}.
\]

The estimates are:

\[
\hat{\theta}_1 = -0.4046,\qquad
\hat{\theta}_2 = -0.3003.
\]

The residual variance is:

\[
\hat{\sigma}^2 = 0.003741.
\]

Both MA coefficients are highly significant. The Ljung-Box test at lag 20 gives
a p-value of 0.8936, so we do not reject the null hypothesis of no residual
autocorrelation. The residuals can therefore be considered white noise, and the
model is valid for the stationary series \(X_t\).

## Question 5 – ARIMA Representation for the Original Series

Since the corrected stationary series is defined as:

\[
X_t = \Delta \log Z_t,
\]

and \(X_t\) follows an ARMA(0,2), the logarithm of the original series follows
an ARIMA(0,1,2) model. The final model can be written as:

\[
\Delta \log Z_t
=
\varepsilon_t + \theta_1 \varepsilon_{t-1}
+ \theta_2 \varepsilon_{t-2},
\]

with:

\[
\hat{\theta}_1 = -0.4046,\quad
\hat{\theta}_2 = -0.3003.
\]

Thus, the selected model for the original observed series is:

\[
\boxed{\log Z_t \sim ARIMA(0,1,2)}.
\]

---

*End of Part II*

---

# Part III – Prediction

## Question 6 – Confidence Region for Future Values

Let \(T\) denote the last observation of the stationary series \(X_t\). We want
the joint confidence region for:

\[
z =
\begin{pmatrix}
X_{T+1} \\
X_{T+2}
\end{pmatrix}.
\]

Under the retained ARMA(0,2) model and Gaussian innovations, the forecast vector
is:

\[
\hat{z} =
\begin{pmatrix}
\widehat{X}_{T+1|T} \\
\widehat{X}_{T+2|T}
\end{pmatrix}.
\]

The confidence region of level \(\alpha\) is:

\[
(z-\hat{z})'\Sigma^{-1}(z-\hat{z}) \leq \chi^2_2(\alpha),
\]

where \(\Sigma\) is the variance-covariance matrix of the two forecast errors.
For the retained ARMA(0,2), written without constant,

\[
X_t=\varepsilon_t+\theta_1\varepsilon_{t-1}
      +\theta_2\varepsilon_{t-2}.
\]

At date \(T\), \(\varepsilon_T\) and \(\varepsilon_{T-1}\) are already in the
information set. Therefore:

\[
\widehat{X}_{T+1|T}
=\theta_1\varepsilon_T+\theta_2\varepsilon_{T-1},
\qquad
\widehat{X}_{T+2|T}
=\theta_2\varepsilon_T.
\]

The corresponding forecast errors are:

\[
e_{T+1|T}=\varepsilon_{T+1},
\qquad
e_{T+2|T}=\varepsilon_{T+2}+\theta_1\varepsilon_{T+1}.
\]

Thus:

\[
\Sigma =
\sigma^2
\begin{pmatrix}
1 & \theta_1 \\
\theta_1 & 1+\theta_1^2
\end{pmatrix}.
\]

The coefficient \(\theta_2\) affects the forecast center, but not this two-step
forecast-error covariance matrix, because the term involving \(\varepsilon_T\)
is known conditionally on the information available at time \(T\).

```{r prediction-region-values}
if (!exists("best_fit")) {
  best_fit <- stats::arima(
    as.numeric(X),
    order = c(0, 0, 2),
    include.mean = FALSE,
    method = "ML"
  )
}

pred_2 <- predict(best_fit, n.ahead = 2)

forecast_mean <- as.numeric(pred_2$pred)
forecast_se <- as.numeric(pred_2$se)

ma_coef <- coef(best_fit)[grep("^ma", names(coef(best_fit)))]
psi1 <- as.numeric(ma_coef[1])
sigma2 <- best_fit$sigma2

Sigma <- sigma2 * matrix(
  c(1, psi1,
    psi1, 1 + psi1^2),
  nrow = 2,
  byrow = TRUE
)

critical_95 <- qchisq(0.95, df = 2)

forecast_table <- data.frame(
  Horizon = c("T+1", "T+2"),
  Forecast = round(forecast_mean, 6),
  Standard_error = round(forecast_se, 6)
)

forecast_table
Sigma
critical_95
```

Numerically, the forecast center is approximately:

\[
\hat{z} =
\begin{pmatrix}
0.0195 \\
0.0150
\end{pmatrix},
\qquad
\chi^2_2(0.95)=5.991.
\]

## Question 7 – Assumptions

This confidence region relies on the following assumptions: the ARMA(0,2) model
is correctly specified for \(X_t=\Delta\log Z_t\), the residuals are white noise,
the innovations are Gaussian, the estimated parameters are treated as known,
and forecasts are conditional on information available up to time \(T\).
Under these assumptions, the two forecast errors form a bivariate Gaussian
vector, so the quadratic form follows a \(\chi^2\) distribution with two degrees
of freedom.

## Question 8 – Graphical Representation for \(\alpha=95\%\)

The following code draws the 95% confidence region for
\((X_{T+1},X_{T+2})\). The region is an ellipse centered on the two-step
forecast mean.

```{r prediction-region-plot, fig.height=5}
theta <- seq(0, 2 * pi, length.out = 400)
eig <- eigen(Sigma, symmetric = TRUE)

ellipse <- t(sapply(theta, function(a) {
  forecast_mean +
    sqrt(critical_95) *
    eig$vectors %*% diag(sqrt(eig$values), nrow = 2) %*%
    c(cos(a), sin(a))
}))

plot(
  ellipse[, 1], ellipse[, 2],
  type = "l",
  lwd = 2,
  col = "#1F4E79",
  xlab = expression(X[T+1]),
  ylab = expression(X[T+2]),
  main = "95% confidence region for future values"
)
points(forecast_mean[1], forecast_mean[2], pch = 19, col = "#B91C1C")
abline(h = 0, v = 0, lty = 2, col = "grey")
grid()
legend(
  "topright",
  legend = c("95% region", "Forecast mean"),
  col = c("#1F4E79", "#B91C1C"),
  lwd = c(2, NA),
  pch = c(NA, 19),
  bty = "n"
)
```

The ellipse is centered around \((0.0195,0.0150)\). Its tilted shape reflects
the covariance between the one-step and two-step forecast errors, which comes
from the moving-average structure of the retained ARMA(0,2) model.

## Question 9 – Additional Information from Another Stationary Series

Suppose another stationary series \(Y_t\) is observed from \(t=1\) to \(T\), and
that \(Y_{T+1}\) is available before \(X_{T+1}\). This information improves the
prediction of \(X_{T+1}\) only if it contains information about the next
innovation of \(X_t\), beyond what is already known at time \(T\). Formally, if
\(\mathcal{I}_T\) is the information set at time \(T\), \(Y_{T+1}\) is useful
when:

\[
E(X_{T+1}\mid \mathcal{I}_T,Y_{T+1})
\neq
E(X_{T+1}\mid \mathcal{I}_T).
\]

For the one-step prediction, this is equivalent to requiring a contemporaneous
link with the innovation of \(X_t\):

\[
\operatorname{Cov}(Y_{T+1},\varepsilon_{T+1}) \neq 0
\]

more precisely after removing the part of \(Y_{T+1}\) predictable from
\(\mathcal{I}_T\). It can be tested by estimating an ARIMAX/transfer model for
\(X_t\) including \(Y_t\), or by first extracting the innovation of \(Y_t\) and
testing whether it is significant in a regression of the innovation of \(X_t\).
A significant coefficient, together with white-noise residuals and improved
out-of-sample forecasts, would show that the faster availability of \(Y_{T+1}\)
improves the prediction of \(X_{T+1}\). Granger causality based only on past
values of \(Y_t\) is related, but the key condition here is this contemporaneous
correlation with the next innovation of \(X_t\).

---

*End of Part III*
